Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-03-30 ApproximareCode.tex
version 4.1

\begin{table*}[]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & Computational Complexity \\ \hline
RS Code & any m disks & m disks & high & high & high \\ \hline
LRC Code & up to m disks & m global disks and r local disks & high & medium & medium \\ \hline
MSR Code & any m disks & m disks & medium & low & very high \\ \hline
Raid 6 & 2 & 2 & low & high & low \\ \hline
SD Code & m disks and s sectors & m disks and s sectors & low & low & low \\ \hline
Approximate Code(Important) & m+s disks & m disks and s sectors & high & high & medium to high \\ \hline
Approximate Code(Ordinary) & m disks & m disks and s sectors & high & high & medium to high \\ \hline
\end{tabular}
\end{table*}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{photo/H264_IPB.pdf}
\caption{A sample of GOPs in H.264}
\label{H264-IPB}
\end{figure}

@@

\section{Approximate Code}
In this section, we introduce the design of Approximate Codes and its properties through a simple example. In order to be general and easy to describe, we use fewer data blocks and more parity blocks (resulting in greater storage overhead). A more optimized parameter selection scheme for practical applications will be introduced in XXX.

>>>>

\begin{table*}[ht]
\centering
\caption{Summary on Various Erasure Codes}
\begin{tabular}{@{}cccccc@{}}
\toprule
Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \midrule
RS($k,r$) Code & any $r$ disks & $r$ disks & high & high & high \\
LRC($k,l,r$) Code & $r+1$ to $r+l$ disks & $l+r$ disks & high & medium & medium \\
MSR($k,r$) Code & any $m$ disks & $m$ disks & medium & low & very high \\
Raid 6 & 2 & 2 & low & high & low \\
SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Ordinary Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{photo/H264_IPB.pdf}
\caption{A sample of GOPs in H.264}
\label{H264-IPB}
\end{figure}

@@

\section{Approximate Code}
In this section, we introduce the design of Approximate Code and its properties through a few simple examples. In order to be general and easy to describe, we use fewer data blocks (resulting in greater storage overhead). A more optimized parameter selection scheme for practical applications will be introduced in \ref{evaluation}.
